An introduction to lightlabsFDS

### 2012-02-29 presentations/lightlabsFDS_mar-2012/pres.tex
Group meetin presentation draft done.

\documentclass[landscape]{foils}
\usepackage{graphicx}
\usepackage{amsmath}
% \usepackage[pdf]{pstricks}
\input defs.tex
\raggedright
\special{! TeXDict begin /landplus90{true}store end }
\renewcommand{\oursection}[1]{
\foilhead[-1.0cm]{#1}
}

@@

% \psset{unit=1.5cm}
% \psset{gridcolor=green, subgridcolor=yellow}
% \begin{center}
% \begin{pspicture}(8,5)
%     \let\psgrid\relax
% 
%     \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (1,2.2)(4,2.8)
%     \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (3,1)(5,4)
%     \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (4,1.4)(7,2)
%     \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (4,3.0)(7,3.6)
%     \rput[B](4,4.1){Device}
%     \psline[linestyle=dashed](1.6,0.6)(1.6,4.0)
%     \rput[B](1.6,4.1){in}
%     \psline[linestyle=dashed](6.4,0.6)(6.4,4.0)
%     \rput[B](6.4,4.1){out}
% \end{pspicture}
% \end{center}
Time-domain issues include
\BIT
\I  Input: clean excitation at input requires an auxiliary simulation
\I  Device: approximations required for material dispersion
\I  Output: overlap integrals must be repeatedly calculated 
        \emph{during} the simulation
\EIT
\newpage

% \begin{center}
% \begin{pspicture}(8,5)
%     \psgrid
% 
%     \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (1,2.2)(4,2.8)
%     \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (3,1)(5,4)
%     \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (4,1.4)(7,2)
%     \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (4,3.0)(7,3.6)
%     \rput[B](4,4.1){Device}
%     \psline[linestyle=dashed](1.6,0.6)(1.6,4.0)
%     \rput[B](1.6,4.1){in}
%     \psline[linestyle=dashed](6.4,0.6)(6.4,4.0)
%     \rput[B](6.4,4.1){out}
% \end{pspicture}
% \end{center}
\BIT
\I  Fundamental problem: trying to use a time-domain solver as a 
        frequency-domain solver.
\I  Additionally, no method to measure simulation error!
\EIT
\newpage

\BIT
\I  Allow direct access to frequency-domain data.
\I  Take care of input and output fields outside of the simulation.
\I  Material dispersion explicitly defined.
\I  Simulation error well defined.
\EIT
\newpage

Picture from paper here.
\BIT
\I  Frequency-domain solver made possible by correct choice of PML and 
        linear algebra algorithm.
\I  See: Wonseok Shin, Shanhui Fan, 
            ``Choice of the perfectly matched layer boundary condition for 
            frequency-domain Maxwell's equations solvers'',
            Journal of Computational Physics (January 2012).
\EIT

@@

\oursection{Hardware}
Hub and spokes picture here.
\BIT
\I  Centralized, shared, custom-tuned server able to deliver the performance
        of a large cluster
\I  Performance achieved via heavily optimized GPU code
\I  Multiple servers can be clustered with nearly $100\%$ computational
        efficiency.
\EIT

>>>>

\documentclass[landscape]{foils}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[pdf]{pstricks}
\input defs.tex
\raggedright
\special{! TeXDict begin /landplus90{true}store end }
\renewcommand{\oursection}[1]{
\foilhead[-1.0cm]{#1}
}

@@

\psset{unit=1.5cm}
\psset{gridcolor=green, subgridcolor=yellow}
\begin{center}
\begin{pspicture}(8,5)
    \let\psgrid\relax

    \psframe*[linecolor=lightgray,fillcolor=lightgray,fillstyle=solid]
        (1,2.2)(4,2.8)
    \psframe*[linecolor=lightgray,fillcolor=lightgray,fillstyle=solid]
        (3,1)(5,4)
    \psframe*[linecolor=lightgray,fillcolor=lightgray,fillstyle=solid]
        (4,1.4)(7,2)
    \psframe*[linecolor=lightgray,fillcolor=lightgray,fillstyle=solid]
        (4,3.0)(7,3.6)
    \rput[B](4,4.2){\textrm{Device}}
    \psline[linestyle=dashed](1.6,0.6)(1.6,4.0)
    \rput[B](1.6,4.2){\textrm{in}}
    \psline[linestyle=dashed](6.4,0.6)(6.4,4.0)
    \rput[B](6.4,4.2){\textrm{out}}
\end{pspicture}
\end{center}
Time-domain issues include
\BIT
\I  Input: clean excitation at input requires an auxiliary simulation
\I  Device: approximations required for material dispersion
\I  Output: overlap integrals must be repeatedly calculated 
        \emph{during} the simulation
\EIT
\newpage

% \begin{center}
\begin{pspicture}(6,5)(-6,0)
    \psgrid

    \psframe[fillstyle=none](-1,2)(1,3)
    \rput(0,2.5){\textrm{TDS}}

    \psline(-2.4,2.5)(-1,2.5)
    \rput[B](-1.6,2.7){$x(t)$}

    \pspolygon[fillcolor=lightgray,fillstyle=solid]
        (-2.4,4)(-2.4,1)(-3.2,0.5)(-3.2,4.5)
    \psline(-4,4)(-3.2,4) \rput(-4.8,4){$X(\omega_1)$}
    \psline(-4,3)(-3.2,3) \rput(-4.8,3){$X(\omega_2)$}
    \psline(-4,2)(-3.2,2) \rput(-4.8,2){$\vdots$}
    \psline(-4,1)(-3.2,1) \rput(-4.8,1){$X(\omega_n)$}

    \psline(2.4,2.5)(1,2.5)
    \rput[B](1.6,2.7){$y(t)$}

    \pspolygon[fillcolor=lightgray,fillstyle=solid]
        (2.4,4)(2.4,1)(3.2,0.5)(3.2,4.5)
    \psline(4,4)(3.2,4) \rput(4.8,4){$Y(\omega_1)$}
    \psline(4,3)(3.2,3) \rput(4.8,3){$Y(\omega_2)$}
    \psline(4,2)(3.2,2) \rput(4.8,2){$\vdots$}
    \psline(4,1)(3.2,1) \rput(4.8,1){$Y(\omega_n)$}
\end{pspicture}
% \end{center}
\BIT
\I  Fundamental problem: trying to use a time-domain solver as a 
        frequency-domain solver.
\I  Additionally, no method to measure simulation error!
\EIT
\newpage

\begin{center}
\begin{pspicture}(6,4)(-6,-2)
    \psgrid

    \psframe[fillstyle=none](-1,2)(1,3)
    \rput(0,2.5){\textrm{FDS}}
    \psline(-2.4,2.5)(-1,2.5)
    \rput(-3.2,2.5){$X(\omega_1)$}
    \psline(2.4,2.5)(1,2.5)
    \rput(3.2,2.5){$Y(\omega_1)$}

    \psframe[fillstyle=none](-1,0.6)(1,1.6)
    \rput(0,1.1){\textrm{FDS}}
    \psline(-2.4,1.1)(-1,1.1)
    \rput(-3.2,1.1){$X(\omega_2)$}
    \psline(2.4,1.1)(1,1.1)
    \rput(3.2,1.1){$Y(\omega_2)$}

    \rput(0,0.2){$\vdots$}

    \psframe[fillstyle=none](-1,-0.4)(1,-1.4)
    \rput(0,-0.9){\textrm{FDS}}
    \psline(-2.4,-0.9)(-1,-0.9)
    \rput(-3.2,-0.9){$X(\omega_n)$}
    \psline(2.4,-0.9)(1,-0.9)
    \rput(3.2,-0.9){$Y(\omega_n)$}
\end{pspicture}
\end{center}
\BIT
\I  Allow direct access to frequency-domain data.
\I  Take care of input and output fields outside of the simulation.
\I  Material dispersion explicitly defined.
\I  Simulation error well defined.
\EIT
\newpage

\begin{center}
% \includegraphics[width=\textwidth]{pml_cutout}
\end{center}
\BIT
\I  Frequency-domain solver made possible by correct choice of PML and 
        linear algebra algorithm.
\I  See: Wonseok Shin, Shanhui Fan, 
            ``Choice of the perfectly matched layer boundary condition for 
            frequency-domain Maxwell's equations solvers'',
            Journal of Computational Physics (January 2012).
\EIT

@@

\oursection{Hardware}
\begin{center}
\begin{pspicture}(6,3)(-6,-3)
    \psgrid
    \rput(0,0){\parbox{5cm}{\begin{center}\textrm{lightlabsFDS\\server}
                            \end{center}}}
    \psline{<->}(-1.2,0.8)(-2.8,1.4) \rput(-3.5,1.5){\textrm{user1}}
    \psline{<->}(-3.2,0)(-1.6,0) \rput(-4,0){\textrm{user2}}
    \psline{<->}(-1.2,-0.8)(-2.8,-1.4) \rput(-3.5,-1.5){\textrm{user3}}
    \psline{<->}(1.2,0.8)(2.8,1.4) \rput(3.5,1.5){\textrm{user4}}
    \psline{<->}(3.2,0)(1.6,0) \rput(4,0){$\vdots$}
    \psline{<->}(1.2,-0.8)(2.8,-1.4) \rput(3.5,-1.5){\textrm{userN}}
\end{pspicture}
\end{center}
\BIT
\I  Centralized, shared, custom-tuned server able to deliver the performance
        of a large cluster
\I  Performance achieved via heavily optimized GPU code
\I  Multiple servers can be clustered with nearly $100\%$ computational
        efficiency.
\EIT
